Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-02-13 parts/example.tex
todo--

\todo{Check section and remove $\procs$ and $\lastprocs$.}

@@

We denote in the following:
$\ctx^2 = \PHstate{f_1, c_0, a_0} \play \PHfrappes{c_0, f_1}{a_0}{a_1} =
\PHstate{f_1, c_0, a_1}$
the state resulting from the play of a scenario concretizing
$\myp^1$ in $\ctx^1$.
As explained in \todo{ref succ-reach},
One can use this resulting state in order to carry on with another
successive reachability,
such as the reachability of $\myp^2 = a_0$ in this case.
The local causality graph used to check the reachability of $\myp^2$
from $ctx^2$ is given in \pref{fig:metazoan-sa}(middle).
The same reasoning allows to conclude that this reachability is true, and
to extract the following set of concretizing scenarios:
$\Delta(\thisB{\myp^2}{\ctx^2}) =
\{ \PHfrappem{a_1, f_1}{c_0}{c_1} \concat \PHfrappem{c_1}{a_1}{a_0} \}$.
We note that once again, two traversals are possible
(by visiting node $a_1$ before or after note $f_1$)
but both output the same scenario, and therefore end up in the same sate
$\ctx^3 = \PHstate{f_1, a_0, c_1}$.
Finally, the last local causality graph $\thisB{\myp^3}{\ctx^3}$,
depicted in \pref{fig:metazoan-sa}(right),
allows to conclude that this final reachability is true.

>>>>

@@

We denote in the following:
$\ctx^2 = \PHstate{f_1, c_0, a_0} \play \PHfrappes{c_0, f_1}{a_0}{a_1} =
\PHstate{f_1, c_0, a_1}$
the state resulting from the play of a scenario concretizing
$\myp^1$ in $\ctx^1$.
As explained in \pref{ssec:ordered-ua},
One can use this resulting state in order to carry on with another
successive reachability,
such as the reachability of $\myp^2 = a_0$ in this case.
The local causality graph used to check the reachability of $\myp^2$
from $ctx^2$ is given in \pref{fig:metazoan-sa}(middle).
The same reasoning allows to conclude that this reachability is true, and
to extract the following set of concretizing scenarios:
$\Delta(\thisB{\myp^2}{\ctx^2}) =
\{ \PHfrappem{a_1, f_1}{c_0}{c_1} \concat \PHfrappem{c_1}{a_1}{a_0} \}$.
We note that once again, two traversals are possible
(by visiting node $a_1$ before or after note $f_1$)
but both output the same scenario, and therefore end up in the same sate
$\ctx^3 = \PHstate{f_1, a_0, c_1}$.
Finally, the last local causality graph $\thisB{\myp^3}{\ctx^3}$,
depicted in \pref{fig:metazoan-sa}(right),
allows to conclude that this final reachability is true.
